Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Added theoretical optimization estimates

\section{SUPERCOP benchmarks}

The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be seen in tables \ref{tbl:supercop:long},
\ref{tbl:supercop:4096}, \ref{tbl:supercop:1536}, \ref{tbl:supercop:576},
\ref{tbl:supercop:64} and \ref{tbl:supercop:8}. The lower the numbers, the
faster and better the algorithms performed in the test.

@@

\section{Measurements of Tahoe data}
% TODO: Fiks denne tabellen så den ikke overflower
% TODO: Sleng inn samme for download
Table \ref{tbl:tahoe:datauploaded} and describes the distribution of the
different input sizes of data that Tahoe-\ac{LAFS} sends to the hash function
when uploading and downloading the test vectors. E.g. to upload the 100 1-byte
files, 15700 hashes had to be calculated, and about 64\% of these were of size
106 byte.

@@

>>>>

\section{SUPERCOP benchmarks}
\label{sec:results:supercop}
The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be seen in tables \ref{tbl:supercop:long},
\ref{tbl:supercop:4096}, \ref{tbl:supercop:1536}, \ref{tbl:supercop:576},
\ref{tbl:supercop:64} and \ref{tbl:supercop:8}. The lower the numbers, the
faster and better the algorithms performed in the test.

@@

\section{Measurements of Tahoe data}
\label{sec:results:tahoedata}

% TODO: Fiks denne tabellen så den ikke overflower
% TODO: Sleng inn samme for download
Table \ref{tbl:tahoe:datauploaded} and describes the distribution of the
different input sizes of data that Tahoe-\ac{LAFS} sends to the hash function
when uploading and downloading the test vectors. E.g. to upload the 100 1-byte
files, 15700 hashes had to be calculated, and about 64\% of these were of size
106 byte.

@@

\subsection{Theoretical optimized results}
These results are calculated using the best \ac{SUPERCOP} results for each
candidate from section \ref{sec:results:supercop}, the exact sizes for each
call to the hash function from section \ref{sec:results:tahoedata}, and
interpolation to estimate the time to hash a length not recorded by
\ac{SUPERCOP}. For lengths above 4096 the results for long data lanegths are
used. The results also assume only one core of the reference processor is used.

\input{tables/tahoe_optimized_p}
\input{tables/tahoe_optimized_g}
